---
title: "Using R in a blog"
author: "Andrie de Vries"
date: 2016-12-21T07:00:00Z
categories: ["R"]
description: ""
featured: ""
featuredalt: ""
featuredpath: ""
linktitle: "using-r-in-blog"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

You can do many things with R, including writing blogs and blog posts.

To build this site, I am using the [Hugo](http://gohugo.io/) static website generator, and the [blogdown](https://github.com/rstudio/blogdown) package.

# Using R and embedding code in the text

This means I can embed R code directly in the text.

The `blogdown::serve_site()` function then renders the content automatically (by first running `rmarkdown` and then letting Hugo buidl the site).

So I can do this:

```{r intro}
1:100
mean(1:100)
```

# Including Plots

You can also embed plots:

```{r pie, fig.cap='A fancy pie chart.'}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```

