---
author: "Andrie de Vries"
title: "Using R in a blog"
type: "post"
date: "2016-12-21"
categories: 
- "R"
description: ""
featured: ""
featuredalt: ""
featuredpath: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

To build this site, I am using the [Hugo](http://gohugo.io/) static website generator, and the [`blogdown`](https://github.com/rstudio/blogdown) package.


```{r echo=FALSE, results='markdown', comment=''}
htmltools::HTML("<!--more-->")
```

# Using R and embedding code in the text



This means I can embed R code directly in the text.

The `blogdown::serve_site()` function then renders the content automatically (by first running `rmarkdown` and then letting Hugo build the site).


So I can do this:

```{r intro}
1:50
mean(1:50)
```

# Including Plots

It is also easy to include plots:

```{r pie, fig.height=3}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```

