---
author: "Andrie de Vries"
title: "The manifold art of Conrad Shawcross"
type: "post"
draft: "false"
date: "2018-04-16"
categories: 
  - "R"
  - "Art"
tags:
  - "Art"
summary: "Inspired by a museum visit, I attempt to recreate the shape of 'manifold', a sculpture by Conrad Shawcross"
thumbnail: images/2018-04/manifold2-9-8.jpg
---
  
```{r setup, include=FALSE}
library(knitr)

knitr::opts_chunk$set(collapse = TRUE)
rgl::setupKnitr()
knit_hooks$set(webgl = rgl::hook_webgl)

```


During April, 2018, I went to visit the [Whitechapel Art Gallery](https://www.whitechapelgallery.org/), a wonderful art gallery in the center of London.

One of the exhibits on display was a piece by [Conrad Shawcross](http://conradshawcross.com/), as part of his exhibition on [Art Capital: Art for the Elizabeth line](http://conradshawcross.com/news-2/) that ran from 13 March to 6 May 2018.

One of the pieces on display was design drawings of his "Manifold" sculpture that is [positioned outside the Moorgate entrance](https://www.victoria-miro.com/news/949) of the Elizabeth line station in London.

He has created a number of pieces in his manifold series, e.g. "Manifold 2 (9:8)" that was [exhibited at the New Art Centre](https://sculpture.uk.com/programme/conrad-shawcross-manifold/) in Salisbury, Wiltshire:

```{r, echo=FALSE}
blogdown::shortcode("figure", src = "/images/2018-04/manifold2-9-8.jpg")
```

At the Whitechapel exhibition, I took a picture of the design drawings for the "Moorgate Manifold", that shows various views, including top, side and cutout views:

```{r, echo=FALSE}
blogdown::shortcode("figure", src = "/images/2018-04/conrad-shawcross-moorgate-manifold.jpg")
```


On close inspection I could see some equations in the drawing:

```{r, echo=FALSE}
blogdown::shortcode("figure", src = "/images/2018-04/conrad-shawcross-equations.jpg")
```

Clearly the original idea was based on a mathematical equation, so I set about trying to replicate this drawing using R code.

## The code

My attempt at replicating the manifold, using code. I had to guess (by experimentation) the initial values of `R1`, `R2` and `H`.  I also had to guess that the decay rate is a function that only applies to the `x` and `y` dimensions.


```{r manifold-equation}
manifold <- function(psi, R1 = 1, R2 = 0.5, H = 7){
  theta <- 5/4 * psi
  x <- R1 * cos(psi) + R2 * cos(psi) * cos(theta)
  y <- R1 * sin(psi) + R2 * sin(psi) * cos(theta)
  z <- H * (1 - psi / (60 * pi)) + R2 * sin(psi)
  
  decay <- function(x){
    x * 2/3 * z^2 / H^2
  }
  
  as.data.frame(cbind(
    x = decay(x),
    y = decay(y),
    z = z
  ))
}
```


Having defined the function, it is straight-forward to generate some values of the data.

```{r generate values}
x <- seq(0, 30 * 7, by = 0.01)
dat <- manifold(x)
head(dat)
```

Now you can plot the results. First, the view from the top down:

```{r ggplot-1, fig.width=6, fig.height=3}
library(ggplot2)
ggplot(dat, aes(x = x, y = y, col = z)) + 
  geom_point(size = 0.1) + 
  coord_equal() + 
  scale_color_gradient(low = "grey80", high = "black") +
  theme_minimal()
```

And next, a sideways view:

```{r ggplot-2, fig.width=6, fig.height=3}
ggplot(dat, aes(x = z, y = x, col = y)) + 
  geom_point(size = 0.1) + 
  scale_color_gradient(low = "grey50", high = "black") +
  coord_equal() + 
  theme_minimal()


```

You can also use `rgl` to create an interactive 3D viewer. Note that you can rotate the object by clicking and dragging on the plot:

```{r webgl, webgl=TRUE}
library(rgl)
with(dat, plot3d(x, y, z))
```


